\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
%\usepackage[margin=0.5in]{geometry}
\usepackage{lingmacros}
\usepackage{tree-dvips}
\title{\vspace{2cm}\line(1,0){300}\\SFWR 3XA3: Problem Statement\\Group 33\\\line(1,0){300}\vspace{8cm}}
\author{Nathan Coit \\ coitn: 400022342 \and Cam Van Ravens \\ vanravec: 400020215 \and Lucas Shanks \\ shanksl: 400029943}
\begin{document}
\maketitle

\clearpage
\tableofcontents
\clearpage

\section{Issues that need to be addressed}
When running a business, one thing you must always track and monitor is your inventory. The inventory of a business is an investment because it is one of most businesses major assets. When tracking inventory, a business must know how much of each product they have and how much of each product they sell over a period of time. Many inventory tracking programs are designed for large companies with expansive inventories, this leads to high costs for the software which many small businesses cannot afford. Our group will develop an app that will better help small businesses manage and track their inventory to save them time and resources.

\section{Importance of problem}
Without an inventory management system, most businesses would run into financial issues very quickly. Inventory tracking information is vital in the ordering of new products, improper tracking of inventory can lead to ordering to much or not enough of a certain product.Users require a easy to use tool to manage and track inventory. The ability to manage a business from anywhere is important, and using a standardized tool provides a easier learning curve for new employees. When new businesses are emerging everyday, the process of inventory management can become tedious, costly, or difficult if done wrong.   

\clearpage
\section{Problem Context}
\subsection{Stakeholders}
The stakeholders our app targets is small businesses with a smaller inventory size without the financial ability to use an inventory management system meant for large companies. These would usually be businesses where the owner themselves would track inventory, thus not being a complete expert in the nuances of inventory tracking.
\subsection{Environment}
Our warehouse inventory management system will run on a service based system where users will be able to access the system over the internet on any platform using a web browser.
\end{document}







